Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/results.tex
fix q

We also find a mass ratio distribution with more support for unequal mass ratios, with power law index 
$\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} 
found with the \textsc{PowerlawPeak} model. This can also be in part related with the harder mass distribution 
as mentioned above. More support for higher mass primaries  -- since total mass is measured better -- increases support for more unequal 
mass ratio binaries.

>>>>

We find a similar mass ratio distribution to what was found with the found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
With the MSpline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}.
